---
output: word_document
editor_options:
chunk_output_type: console
---

```{r setup, include=FALSE}
# Load necessary libraries
library(tidyverse)    # Data manipulation & visualization
library(summarytools) # Summary statistics
library(ggplot2)      # Advanced visualizations
library(knitr)        # Tables formatting
library(kableExtra)   # Improved table aesthetics
library(corrplot)     # Correlation matrix
library(Amelia)       # Missing values visualization
library(caret)        # Feature selection & preprocessing
library(randomForest) # Feature importance analysis

# Set global options
options(scipen = 999)  # Disable scientific notation
knitr::opts_chunk$set(echo = TRUE)  # Display code in output
```


# ** Descriptive statistical analysis  **

## Load the Data
```{r}

dataset_path <- "descriptive_statistics/games.csv"
steam_data <- read_csv(dataset_path)
```
The dataset contains detailed information about Steam games, including their genres, release dates, prices, and player statistics.

## Dataset Overview
The dataset contains detailed information about Steam games, including their genres, release dates, prices, and player statistics.

Display the first few rows
```{r}
head(steam_data)
```
Display the structure of the dataset
```{r}
str(steam_data)
```
Display column names
```{r}
names(steam_data)
```
Get dimensions of the dataset
```{r}
dim(steam_data)
n <- dim(steam_data)[1]
K <- dim(steam_data)[2]

cat("Number of rows (games):", n, "\n")
cat("Number of columns (features):", K, "\n")
```
## Exploratory Data Analysis

Distribution of Numerical Variables
```{r}
# Select numerical columns
numeric_cols <- steam_data %>% select(where(is.numeric))

# Histogram of numerical variables
numeric_cols %>%
  gather() %>%
  ggplot(aes(value)) +
  facet_wrap(~ key, scales = "free") +
  geom_histogram(bins = 30, fill = "blue", color = "black") +
  theme_minimal() +
  labs(title = "Distribution of Numerical Variables", x = "Value", y = "Frequency")
```

Distribution of Categorical Variables
```{r}
# Select categorical columns
categorical_cols <- steam_data %>% select(where(is.character))

# Bar charts for categorical features
categorical_cols %>%
  gather() %>%
  ggplot(aes(value)) +
  facet_wrap(~ key, scales = "free") +
  geom_bar(fill = "darkgreen", color = "black", alpha = 0.7) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "Distribution of Categorical Variables",
       x = "Category",
       y = "Count",
       caption = "Bar plots showing the distribution of categorical features in the dataset.")
```
## Correlation Analysis

Correlation Matrix for Numerical Features
```{r}
# Compute correlation matrix
cor_matrix <- cor(numeric_cols, use = "complete.obs")

# Visualize correlations
corrplot(cor_matrix,
         method = "color",
         type = "upper",
         tl.col = "black",
         tl.srt = 45,
         title = "Correlation Matrix of Numerical Variables",
         mar = c(0, 0, 1, 0))


```

## Missing Values Analysis
```{r}
# Visualizing missing data
# Visualizing missing data
missmap(steam_data,
        main = "Missing Values Map",
        col = c("red", "grey"),
        legend = TRUE,
        margins = c(10, 5))
```
## Summary Statistics

Summary of Numerical Variables
```{r}
summary(numeric_cols) %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

Summary of Categorical Variables
```{r}
summary(categorical_cols) %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

## Conclusion
This exploratory analysis provides a detailed overview of the Steam Games dataset. Key findings include:

* The distribution of numerical and categorical variables.
* The presence of missing values and their distribution.
* Correlations between numerical features.

Further analysis could involve predictive modeling, clustering, or deeper insights into specific features like game genres or pricing strategies.